Value Ordering, Discrepancies, and Restarts in Subgraph Solvers: \\ Some Half-Baked Mucking Around

### 2017-10-22 paper/paper.tex
Useful things

?? do a more detailed breakdown by family

?? maybe some engineering aspects: look at performance with restarts on degree, and at restarts
without nogood recording, and what happens without nogoods in \cref{figure:scatter-nogoods}.

\begin{figure}[tb]
    \centering
    \includegraphics*{gen-graph-scatter-nogoods.pdf}

@@

\begin{figure}[tb]
    \centering
    \includegraphics*{gen-graph-scatter-overheads.pdf}

    \caption{Is nogood recording and restarting expensive?}
    \label{figure:scatter-overhead}
\end{figure}

\begin{figure}[tb]
    \centering
    \includegraphics*{gen-graph-restart-policies.pdf}

    \caption{Different restart policies}
    \label{figure:restart-policies}
\end{figure}

\begin{figure}[tb]
    \centering
    \includegraphics*{gen-graph-scatter-geometric.pdf}

    \caption{Geometric instead of Luby}
    \label{figure:scatter-geometric}
\end{figure}

>>>>

\begin{figure}[tb]
    \centering
    \includegraphics*{gen-graph-scatter-by-family.pdf}

    \caption{Instance by instance comparison of the basic algorithm with the degree heuristic,
    versus degree-biased + restarts, showing only satisfiable instances, on a family by family
    basis.}
    \label{figure:scatter-by-family}
\end{figure}

?? do a more detailed breakdown by family, \cref{figure:scatter-by-family}

?? maybe some engineering aspects: look at what happens without nogoods in
\cref{figure:scatter-nogoods}, and at performance with restarts on degree in
\cref{figure:scatter-overheads}.

\begin{figure}[p]
    \centering
    \includegraphics*{gen-graph-scatter-nogoods.pdf}

@@

\begin{figure}[p]
    \centering
    \includegraphics*{gen-graph-scatter-overheads.pdf}

    \caption{Is nogood recording expensive?}
    \label{figure:scatter-overheads}
\end{figure}

\begin{figure}[p]
    \centering
    \includegraphics*{gen-graph-restart-policies.pdf}

    \caption{Different restart policies.}
    \label{figure:restart-policies}
\end{figure}
